Performance Models for Data Transfers: A Case Study with Molecular Chemistry Kernels

### 2019-04-02 Article/article.tex
tikz diagrams

\usepackage[utf8]{inputenc}
%%\usepackage{amsmath}
%%\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{threeparttable}
\usepackage{graphicx}
\usepackage{color}
\usepackage{paralist}
\usepackage{framed}
\usepackage{caption}
%%\usepackage{subcaption}
\captionsetup{compatibility=false}
\usepackage{todonotes}
\usepackage{subfig}

@@

\end{itemize}
\todo[inline]{SKumar: equivalent tikz figure}
\begin{tabular}{|l|l|l|}
\hline
Task & Comm Time & Comp Time\\ \hline
A & 3 & 2\\ \hline
B & 1 & 3\\ \hline
C & 4 & 4\\ \hline
D & 2 & 1\\ \hline
\end{tabular}
	\begin{figure}[htb]
	\centering
%% 	\subfloat[Optimal schedule]{
		\begin{tikzpicture}[decoration={brace, amplitude=5},scale=0.5, every node/.style={scale=0.5}]
		\tikzstyle{legend}=[below=0.1, anchor=mid] 	
		\node(t1) at (0,0) {};

	    \node[above right=0.4cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=9cm, draw=white, fill=white, scale=1.5](IMC) {$Infinite Memory Capacity$};

@@

 		\node(t1) at ([shift={(0, -3.8)}] t1.mid) {};   
%%	    \node[above right=0cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=9cm, draw=white, fill=white, scale=1.5](MC) {$Memory Capacity=6$}; 
	    \node[above right=0.4cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=9cm, draw=white, fill=white, scale=1.5](IMC) {$Memory Capacity=6$};

@@

		\end{tikzpicture}
%%	} %\hspace{0.01\textwidth} %\hfill% or \hspace{5mm} or \hspace{0.3\textwidth}
%%	\subfloat[HP schedule]{
%%		\begin{tikzpicture}[decoration={brace, amplitude=5},scale=1.8, every node/.style={scale=1.8}]
%%		\node(t1) at (0,0) {};      		
%%		
%%		\node[above right=0cm and 0cm of t1.mid, draw, minimum height=0.5cm, minimum width=0.618cm,draw,fill=white](t2) {$Y$};
%%		
%%		\node[above right=0.5cm and 0cm of t2.north west, draw, minimum height=0.5cm, minimum width=1.618cm,draw,fill=white](t3) {$X$};								
%%		
%%		\tikzstyle{legend}=[below=0.35, anchor=mid] 	
%%		\draw[->] (-0.1, -0.1) -- (0, -0.1)  node[legend,scale=0.65]{$0$} --(0.618,-0.1) node [legend,scale=0.65]{$\tfrac{1}{\phi}$} --(1.618,-0.1) node [legend,scale=0.65]{$\phi$} --(2, -0.1) node[right,scale=0.65]{$t$}; 
%%		
%%		\foreach \x in {0cm, 0.618cm, 1.618cm} \draw (\x, -0.12) -- (\x, -0.08);
%%		%%			To align both figures of subfloat -- an object without drawing at the same depth
%%		
%%		\path (-0.1, -0.5) -- (2, -0.5);
%%		
%%		\end{tikzpicture}
%%	} 
	\caption{ \label{fig:staticSchedules} Static.}
\end{figure}

\begin{figure}[htb]

	\includegraphics[scale=0.05]{Figs/staticOrderSchedules}
			\caption{Task set and schedules where orders are precomputed based on different heuristics.}
	\label{fig:staticOrderExample}
\end{figure}

Fig~\ref{fig:staticOrderExample} shows schedules for all proposed heuristics of this class for task set of Table (ref).
\subsection{Dynamic Selection}
%%%%string alg_name="largest_communication_task_respects_memory_restriction";
%%%%string alg_name="smallest_communication_task_respects_memory_restriction";
%%%%string alg_name="maximum_accelerated_task_respects_memory_restriction";

@@

\end{itemize}
\todo[inline]{SKumar: equivalent tikz figure}

\begin{figure}[htb]

\includegraphics[scale=0.05]{Figs/dynamiSelectionSchedules}
\caption{Task set and schedules where orders are precomputed based on different heuristics.}
\label{fig:dynamicSelectionExample}
\end{figure}

Fig~\ref{fig:dynamicSelectionExample} shows schedules for all proposed heuristics of this class for task set of Table (ref).

@@

\todo[inline]{SKumar: equivalent tikz figure}
\begin{figure}[htb]
\includegraphics[scale=0.05]{Figs/staticOrderDynamicCorrectionsSchedules}
\caption{Task set and schedules where orders are precomputed based on different heuristics.}
\label{fig:staticOrderDynamicCorrectionsExample}
\end{figure}

>>>>

\usepackage[utf8]{inputenc}
%%\usepackage{amsmath}
%%\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{threeparttable}
\usepackage{graphicx}
\usepackage{color}
\usepackage{paralist}
\usepackage{framed}
\usepackage{caption}
%%\usepackage{subcaption}
\captionsetup{compatibility=false}
\usepackage{todonotes}
\usepackage{subfig}
\usepackage{multirow}

@@

\end{itemize}
\todo[inline]{SKumar: update short name of each strategy in tikz}
	\begin{table}[htb]
	\begin{center}

		\begin{tabular}{|c|c|c|}
		\hline
		\multirow{2}{*}{Task} & Comm Time & \multirow{2}{*}{Comp Time}\\ 
		&=Comm Volume& \\ \hline
		A & 3 & 2\\ \hline
		B & 1 & 3\\ \hline
		C & 4 & 4\\ \hline
		D & 2 & 1\\ \hline
		\end{tabular}
	\caption{\label{tab:staticOrderExample} A task set for static order schedules.}
	\end{center}
	\end{table}

	\begin{figure}[htb]
	\centering
%% 	\subfloat[Optimal schedule]{
		\begin{tikzpicture}[decoration={brace, amplitude=5},scale=0.6, every node/.style={scale=0.6}]
		\tikzstyle{legend}=[below=0.1, anchor=mid] 	
		\node(t1) at (0,0) {};

	    \node[above right=0.6cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=9cm, draw=white, fill=white, scale=1.5](IMC) {$Infinite Memory Capacity$}; 	    				
%%	    \node[above right=0.4cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=9cm, draw=white, fill=white, scale=1.5](IMC) {$Infinite Memory Capacity$};

@@

 		\node(t1) at ([shift={(0, -3.8)}] t1.mid) {};   
%%	    \node[above right=0cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=9cm, draw=white, fill=white, scale=1.5](MC) {$Memory Capacity=6$}; 
%%	    \node[above right=0.4cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=9cm, draw=white, fill=white, scale=1.5](IMC) {$Memory Capacity=6$};	   
	    \node[above right=0.6cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=9cm, draw=white, fill=white, scale=1.5](IMC) {$Memory Capacity=6$};

@@

		\end{tikzpicture}

	\caption{ \label{fig:staticOrderExample} Different static order heuristic schedules for Table~\ref{tab:staticOrderExample}.}
\end{figure}

%%\begin{figure}[htb]
%%	
%%	\includegraphics[scale=0.05]{Figs/staticOrderSchedules}
%%			\caption{Task set and schedules where orders are precomputed based on different heuristics.}
%%	\label{fig:staticOrderExample}
%%\end{figure}

Fig~\ref{fig:staticOrderExample} shows schedules for all proposed heuristics of this class for task set of Table~\ref{tab:staticOrderExample}.
\subsection{Dynamic Selection}
%%%%string alg_name="largest_communication_task_respects_memory_restriction";
%%%%string alg_name="smallest_communication_task_respects_memory_restriction";
%%%%string alg_name="maximum_accelerated_task_respects_memory_restriction";

@@

\end{itemize}
%%\todo[inline]{SKumar: equivalent tikz figure}
	\begin{table}[htb]
	\begin{center}

		\begin{tabular}{|c|c|c|}
			\hline
			\multirow{2}{*}{Task} & Comm Time & \multirow{2}{*}{Comp Time}\\ 
			&=Comm Volume& \\ \hline
			A & 3 & 2\\ \hline
			B & 1 & 6\\ \hline
			C & 4 & 6\\ \hline
			D & 5 & 1\\ \hline
		\end{tabular}
		\caption{\label{tab:dynamicSelectionExample} A task set for dynamic schedules.}
	\end{center}
\end{table}

\begin{figure}[htb]
	\centering
	%% 	\subfloat[Optimal schedule]{
	\begin{tikzpicture}[decoration={brace, amplitude=5},scale=0.6, every node/.style={scale=0.6}]
	\tikzstyle{legend}=[below=0.1, anchor=mid] 	
	\node(t1) at (0,0) {};  
	\node[above right=0.6cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=15cm, draw=white, fill=white, scale=1.5](IMC) {$Memory Capacity=6$};

	\node[below right=0cm and 0cm of b11.south east, minimum height=0.5cm, minimum width=6cm,draw,fill=white](b12) {$B$};

	\node[above right=0cm and 0cm of b11.south east, minimum height=0.5cm, minimum width=5cm,draw,fill=white](d11) {$D$};

	\node[below right=0cm and 0cm of b12.north east, minimum height=0.5cm, minimum width=1cm,draw,fill=white](d12) {$D$};

	\node[above right=0cm and 0cm of d12.north east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](a11) {$A$};

	\node[below right=0cm and 0cm of a11.south east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](a12) {$A$};

	\node[above right=0cm and 0cm of a12.north east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c11) {$C$};

	\node[below right=0cm and 0cm of c11.south east, minimum height=0.5cm, minimum width=6cm,draw,fill=white](c12) {$C$};

	\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
	-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.65]{$0$}
	-- ([shift={(1, -0.65)}] t1.mid)node[legend,scale=0.65]{$1$}
	-- ([shift={(6, -0.65)}] t1.mid)node[legend,scale=0.65]{$6$}
	-- ([shift={(7, -0.65)}] t1.mid)node[legend,scale=0.65]{$7$}
	-- ([shift={(8, -0.65)}] t1.mid)node[legend,scale=0.65]{$8$}
	-- ([shift={(11, -0.65)}] t1.mid)node[legend,scale=0.65]{$11$}         
	-- ([shift={(13, -0.65)}] t1.mid)node[legend,scale=0.65]{$13$}                                      
	-- ([shift={(17, -0.65)}] t1.mid)node[legend,scale=0.65]{$17$}
	-- ([shift={(23, -0.65)}] t1.mid)node[legend,scale=0.65]{$23$}
	-- ([shift={(25.1, -0.65)}] t1.mid)node[right,scale=0.65]{$t$};

	\foreach \x in {0, 1, 6, 7, 8, 11, 13, 17, 23} \draw ([shift={(\x, -0.61)}] t1.mid) -- ([shift={(\x, -0.69)}] t1.mid);

	%% schedule of third heuristic		
	\node(t1) at ([shift={(0, -1.8)}] t1.mid) {};                		
	\node[above right=0cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=1cm,draw,fill=white](b21) {$B$};

	\node[below right=0cm and 0cm of b21.south east, minimum height=0.5cm, minimum width=6cm,draw,fill=white](b22) {$B$};

	\node[above right=0cm and 0cm of b21.south east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](a21) {$A$};

	\node[below right=0cm and 0cm of b22.north east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](a22) {$A$};

	\node[above right=0cm and 0cm of a22.north east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c21) {$C$};

	\node[below right=0cm and 0cm of c21.south east, minimum height=0.5cm, minimum width=6cm,draw,fill=white](c22) {$C$};

	\node[above right=0cm and 0cm of c22.north east, minimum height=0.5cm, minimum width=5cm,draw,fill=white](d21) {$D$};

	\node[below right=0cm and 0cm of d21.south east, minimum height=0.5cm, minimum width=1cm,draw,fill=white](d22) {$D$};

		\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
		-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.65]{$0$}
		-- ([shift={(1, -0.65)}] t1.mid)node[legend,scale=0.65]{$1$}
		-- ([shift={(4, -0.65)}] t1.mid)node[legend,scale=0.65]{$4$}
		-- ([shift={(7, -0.65)}] t1.mid)node[legend,scale=0.65]{$7$}
		-- ([shift={(9, -0.65)}] t1.mid)node[legend,scale=0.65]{$9$}
		-- ([shift={(13, -0.65)}] t1.mid)node[legend,scale=0.65]{$13$}         
		-- ([shift={(19, -0.65)}] t1.mid)node[legend,scale=0.65]{$19$}                                      
		-- ([shift={(24, -0.65)}] t1.mid)node[legend,scale=0.65]{$24$}
		-- ([shift={(25, -0.65)}] t1.mid)node[legend,scale=0.65]{$25$}
		-- ([shift={(25.1, -0.65)}] t1.mid)node[right,scale=0.65]{$t$};

	\foreach \x in {0, 1, 4, 7, 9, 13, 19, 24, 25} \draw ([shift={(\x, -0.61)}] t1.mid) -- ([shift={(\x, -0.69)}] t1.mid);

	\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$BACD$};

	\node[below right=0cm and 0cm of b31.south east, minimum height=0.5cm, minimum width=6cm,draw,fill=white](b32) {$B$};

	\node[above right=0cm and 0cm of b31.south east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c31) {$C$};

	\node[below right=0cm and 0cm of b32.north east, minimum height=0.5cm, minimum width=6cm,draw,fill=white](c32) {$C$};

	\node[above right=0cm and 0cm of c32.north east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](a31) {$A$};

	\node[above right=0cm and 0cm of a32.north east, minimum height=0.5cm, minimum width=5cm,draw,fill=white](d31) {$D$};

	\node[below right=0cm and 0cm of d31.south east, minimum height=0.5cm, minimum width=1cm,draw,fill=white](d32) {$D$};

		\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
		-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.65]{$0$}
		-- ([shift={(1, -0.65)}] t1.mid)node[legend,scale=0.65]{$1$}
		-- ([shift={(5, -0.65)}] t1.mid)node[legend,scale=0.65]{$5$}
		-- ([shift={(7, -0.65)}] t1.mid)node[legend,scale=0.65]{$7$}
		-- ([shift={(13, -0.65)}] t1.mid)node[legend,scale=0.65]{$13$}
		-- ([shift={(16, -0.65)}] t1.mid)node[legend,scale=0.65]{$16$}         
		-- ([shift={(18, -0.65)}] t1.mid)node[legend,scale=0.65]{$18$}                                      
		-- ([shift={(23, -0.65)}] t1.mid)node[legend,scale=0.65]{$23$}
		-- ([shift={(24, -0.65)}] t1.mid)node[legend,scale=0.65]{$24$}
		-- ([shift={(25.1, -0.65)}] t1.mid)node[right,scale=0.65]{$t$};

	\foreach \x in {0, 1, 5, 7, 13, 16, 18, 23, 24} \draw ([shift={(\x, -0.61)}] t1.mid) -- ([shift={(\x, -0.69)}] t1.mid);

	\end{tikzpicture}
		\caption{ \label{fig:dynamicSelectionExample} Different dynamic heuristic schedules for a task set of Table~\ref{tab:dynamicSelectionExample}.}
	\end{figure}

%%\begin{figure}[htb]
%%
%%\includegraphics[scale=0.05]{Figs/dynamiSelectionSchedules}
%%\caption{Task set and schedules where orders are precomputed based on different heuristics.}
%%\label{fig:dynamicSelectionExample}
%%\end{figure}

Fig~\ref{fig:dynamicSelectionExample} shows schedules for all proposed heuristics of this class for task set of Table~\ref{tab:dynamicSelectionExample}.

@@

	\begin{table}[htb]
	\begin{center}

		\begin{tabular}{|c|c|c|}
			\hline
			\multirow{2}{*}{Task} & Comm Time & \multirow{2}{*}{Comp Time}\\ 
			&=Comm Volume& \\ \hline
			A & 4 & 1\\ \hline
			B & 2 & 6\\ \hline
			C & 8 & 8\\ \hline
			D & 5 & 4\\ \hline
			E & 3 & 2\\ \hline
		\end{tabular}
		\caption{\label{tab:staticOrderDynamicCorrectionsExample} A task set for static order dynamic corrections schedules.}
	\end{center}
\end{table}

\begin{figure}[htb]
	\centering
	%% 	\subfloat[Optimal schedule]{
	\begin{tikzpicture}[decoration={brace, amplitude=5},scale=0.3, every node/.style={scale=0.3}]
	\tikzstyle{legend}=[below=0.1, anchor=mid] 	
	\node(t1) at (0,0) {};  
	\node[above right=1.2cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=20cm, draw=white, fill=white, scale=1.5](MC) {Optimal Order with Infinite Memory = $BCDAE$};
	\node[above right=0.6cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=20cm, draw=white, fill=white, scale=1.5](MC) {$Memory Capacity=9$};

	\node[above right=0cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=2cm,draw,fill=white](b11) {$B$};

	\node[below right=0cm and 0cm of b11.south east, minimum height=0.5cm, minimum width=6cm,draw,fill=white](b12) {$B$};

	\node[above right=0cm and 0cm of b11.south east, minimum height=0.5cm, minimum width=5cm,draw,fill=white](d11) {$D$};

	\node[below right=0cm and 0cm of b12.north east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](d12) {$D$};

	\node[above right=0cm and 0cm of b12.north east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](a11) {$A$};

	\node[below right=0cm and 0cm of a11.south east, minimum height=0.5cm, minimum width=1cm,draw,fill=white](a12) {$A$};

	\node[above right=0cm and 0cm of d12.north east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](e11) {$E$};

	\node[below right=0cm and 0cm of e11.south east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](e12) {$E$};

	\node[above right=0cm and 0cm of e12.north east, minimum height=0.5cm, minimum width=8cm,draw,fill=white](c11) {$C$};

	\node[below right=0cm and 0cm of c11.south east, minimum height=0.5cm, minimum width=8cm,draw,fill=white](c12) {$C$};

		\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
		-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.65]{$0$}
		-- ([shift={(2, -0.65)}] t1.mid)node[legend,scale=0.65]{$2$}
		-- ([shift={(7, -0.65)}] t1.mid)node[legend,scale=0.65]{$7$}
		-- ([shift={(8, -0.65)}] t1.mid)node[legend,scale=0.65]{$8$}
		-- ([shift={(12, -0.65)}] t1.mid)node[legend,scale=0.65]{$12$}
		-- ([shift={(13, -0.65)}] t1.mid)node[legend,scale=0.65]{$13$}         
		-- ([shift={(15, -0.65)}] t1.mid)node[legend,scale=0.65]{$15$}                                      
		-- ([shift={(17, -0.65)}] t1.mid)node[legend,scale=0.65]{$17$}
		-- ([shift={(25, -0.65)}] t1.mid)node[legend,scale=0.65]{$25$}
		-- ([shift={(33, -0.65)}] t1.mid)node[legend,scale=0.65]{$33$}
		-- ([shift={(33.1, -0.65)}] t1.mid)node[right,scale=0.65]{$t$};

	\foreach \x in {0, 2, 7, 8, 12, 13, 15, 17, 25, 33} \draw ([shift={(\x, -0.61)}] t1.mid) -- ([shift={(\x, -0.69)}] t1.mid);

	\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$BDAEC$};

	%% schedule of second heuristic		
	\node(t1) at ([shift={(0, -1.8)}] t1.mid) {};

	\node[above right=0cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=2cm,draw,fill=white](b21) {$B$};

	\node[below right=0cm and 0cm of b21.south east, minimum height=0.5cm, minimum width=6cm,draw,fill=white](b22) {$B$};

	\node[above right=0cm and 0cm of b21.south east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](e21) {$E$};

	\node[below right=0cm and 0cm of b22.north east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](e22) {$E$};

	\node[above right=0cm and 0cm of e21.south east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](a21) {$A$};

	\node[below right=0cm and 0cm of e22.north east, minimum height=0.5cm, minimum width=1cm,draw,fill=white](a22) {$A$};

	\node[above right=0cm and 0cm of a21.south east, minimum height=0.5cm, minimum width=5cm,draw,fill=white](d21) {$D$};

	\node[below right=0cm and 0cm of d21.south east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](d22) {$D$};

	\node[above right=0cm and 0cm of d22.north east, minimum height=0.5cm, minimum width=8cm,draw,fill=white](c21) {$C$};

	\node[below right=0cm and 0cm of c21.south east, minimum height=0.5cm, minimum width=8cm,draw,fill=white](c22) {$C$};

		\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
		-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.65]{$0$}
		-- ([shift={(2, -0.65)}] t1.mid)node[legend,scale=0.65]{$2$}
		-- ([shift={(5, -0.65)}] t1.mid)node[legend,scale=0.65]{$5$}
		-- ([shift={(8, -0.65)}] t1.mid)node[legend,scale=0.65]{$8$}
		-- ([shift={(9, -0.65)}] t1.mid)node[legend,scale=0.65]{$9$}
		-- ([shift={(10, -0.65)}] t1.mid)node[legend,scale=0.65]{$10$}
		-- ([shift={(11, -0.65)}] t1.mid)node[legend,scale=0.65]{$11$}         
		-- ([shift={(14, -0.65)}] t1.mid)node[legend,scale=0.65]{$14$}                                      
		-- ([shift={(18, -0.65)}] t1.mid)node[legend,scale=0.65]{$18$}
		-- ([shift={(26, -0.65)}] t1.mid)node[legend,scale=0.65]{$26$}
		-- ([shift={(34, -0.65)}] t1.mid)node[legend,scale=0.65]{$34$}
		-- ([shift={(34.1, -0.65)}] t1.mid)node[right,scale=0.65]{$t$};

	\foreach \x in {0, 2, 5, 8, 9, 10, 11, 14, 18, 26, 34} \draw ([shift={(\x, -0.61)}] t1.mid) -- ([shift={(\x, -0.69)}] t1.mid);

	\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$BEADC$};

	%% schedule of third heuristic		
	\node(t1) at ([shift={(0, -1.8)}] t1.mid) {};

	\node[above right=0cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=2cm,draw,fill=white](b31) {$B$};

	\node[below right=0cm and 0cm of b31.south east, minimum height=0.5cm, minimum width=6cm,draw,fill=white](b32) {$B$};

	\node[above right=0cm and 0cm of b31.south east, minimum height=0.5cm, minimum width=5cm,draw,fill=white](d31) {$D$};

	\node[below right=0cm and 0cm of b32.north east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](d32) {$D$};

	\node[above right=0cm and 0cm of b32.north east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](e31) {$E$};

	\node[below right=0cm and 0cm of d32.north east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](e32) {$E$};

	\node[above right=0cm and 0cm of d32.north east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](a31) {$A$};

	\node[below right=0cm and 0cm of a31.south east, minimum height=0.5cm, minimum width=1cm,draw,fill=white](a32) {$A$};

	\node[above right=0cm and 0cm of a32.north east, minimum height=0.5cm, minimum width=8cm,draw,fill=white](c31) {$C$};

	\node[below right=0cm and 0cm of c31.south east, minimum height=0.5cm, minimum width=8cm,draw,fill=white](c32) {$C$};

		\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
		-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.65]{$0$}
		-- ([shift={(2, -0.65)}] t1.mid)node[legend,scale=0.65]{$2$}
		-- ([shift={(7, -0.65)}] t1.mid)node[legend,scale=0.65]{$7$}
		-- ([shift={(8, -0.65)}] t1.mid)node[legend,scale=0.65]{$8$}
		-- ([shift={(11, -0.65)}] t1.mid)node[legend,scale=0.65]{$11$}
		-- ([shift={(12, -0.65)}] t1.mid)node[legend,scale=0.65]{$12$}         
		-- ([shift={(14, -0.65)}] t1.mid)node[legend,scale=0.65]{$14$}                                      
		-- ([shift={(16, -0.65)}] t1.mid)node[legend,scale=0.65]{$16$}
		-- ([shift={(17, -0.65)}] t1.mid)node[legend,scale=0.65]{$17$}
		-- ([shift={(25, -0.65)}] t1.mid)node[legend,scale=0.65]{$25$}
		-- ([shift={(33, -0.65)}] t1.mid)node[legend,scale=0.65]{$33$}
		-- ([shift={(33.1, -0.65)}] t1.mid)node[right,scale=0.65]{$t$};

	\foreach \x in {0, 2, 7, 8, 11, 12, 14, 16, 17, 25, 33} \draw ([shift={(\x, -0.61)}] t1.mid) -- ([shift={(\x, -0.69)}] t1.mid);

	\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$BDEAC$};

	\end{tikzpicture}
	\caption{ \label{fig:staticOrderDynamicCorrectionsExample} Different static order dynamic corrections heuristic schedules for a task set of Table~\ref{tab:staticOrderDynamicCorrectionsExample}.}
\end{figure}

%%\begin{figure}[htb]
%%\includegraphics[scale=0.05]{Figs/staticOrderDynamicCorrectionsSchedules}
%%\caption{Task set and schedules where orders are precomputed based on different heuristics.}
%%\label{fig:staticOrderDynamicCorrectionsExample}
%%\end{figure}
